NSF-Soft-Search: Two Datasets to Study the Identification and Production of Research Software

### 2023-02-18 paper/paper.qmd
Update paper after title change

---
title: "Searching for Software in NSF Awards"
author:
  - name: "Eva Maxfield Brown"
    email: evamxb@uw.edu
    orcid: 0000-0003-2564-0373
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA
  - name: "Lindsey Schwartz"
    email: lsschwar@uw.edu
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA
  - name: "Richard Lewei Huang"
    email: lwhuang@uw.edu
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA
  - name: "Nicholas Weber"
    email: nmweber@uw.edu
    orcid: 0000-0002-6008-3763
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA

@@

# acm-specific metadata
acm-metadata:
  # comment this out to make submission anonymous
  anonymous: true

>>>>

---
title: "NSF-Soft-Search: Two Datasets to Study the Identification and Production of Research Software"
author:
  # - name: Anonymous Submission
  - name: "Eva Maxfield Brown"
    email: evamxb@uw.edu
    orcid: 0000-0003-2564-0373
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA
  - name: "Lindsey Schwartz"
    email: lsschwar@uw.edu
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA
  - name: "Richard Lewei Huang"
    email: lwhuang@uw.edu
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA
  - name: "Nicholas Weber"
    email: nmweber@uw.edu
    orcid: 0000-0002-6008-3763
    affliation:
        name: University of Washington Information School
        city: Seattle
        state: Washington
        country: USA

@@

# acm-specific metadata
acm-metadata:
  # comment this out to make submission anonymous
  # anonymous: true
